\input{../../content_files/input_files/settings}
\title{Cover Letter}
\input{../../content_files/input_files/variables}
\input{../../content_files/input_files/contact_details}
% \photo[80pt][0.7pt]{../assets/portraits/ivar_cashin_eriksson_udsnit96I7922.jpg}

%----------------------------------------------------------------------------------------
\newcommand{\role}{Senior Manager, Machine Learning Engineer}
\newcommand{\company}{Novo Holdings}
%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle


\section{Introduction}
To whom it may concern, I wish to apply for the role as \role{}.
I am motivated to transition from my current role as Senior Data Science Consultant at Valcon back into an environment with more long-term engagements, and I believe \company{} could be the perfect fit.
I have previously worked in the life science and finance industries as a Data Scientist.
As a data science reseracher at RaySearch Laboratories I attained an in-depth grasp of radiotherapy for cancer treatment and innovatively applied machine learning to the domain.
In the finance sector, I worked as a developer for a small Swedish proprietary trading firm and in a consultancy capacity for a private equity company, helping them evolve their companies' data science offerings.
The meaningful impact on patient well-being, and the attention to detail these roles provided respectively, deeply motivated me.
This is why I choose to apply.

\section{Work Experience}
I am currently working at Valcon as a Senior Data Scientist Consultant.
My daily work involves a wide variety of data science tasks and finding insights in any sort of data, from any sector.
Examples of previous work include, clustering, churn analysis, NLP, and deep learning, in industries such as pension, manufacturing, and pharmaceuticals.
Being a consultant means that the projects always have a business angle and that being able to present the results in an understandable manner is as important as the results themselves.

\hspace{7 mm} As a consultant, I am exposed to a range of different problems in many sectors, and it is important to quickly understand the task at hand.
I design machine learning models to solve the business problems posed in a long-term, impact oriented way.
Being the lead data scientist means having a wide knowledge base within data science and a great imagination.
I need to set a vision for the project, and architect, implement, and deploy the solution, all within a limited budget.

\hspace{7 mm} In addition to my work on projects, I have played a large role in developing the data team at Valcon.
As part of my work, I have been deeply involved in the hiring process to ensure we have the right mix of people.
I have also made sure to up-skill my colleagues by constructing trainings in machine learning explainability and Git.
I am currently the designated mentor to 2 other data scientists in the team.

\hspace{7 mm} My previous experience leading the development of production grade machine learning solutions, and business oriented decision-making, means that I would quickly become a productive member of the team at \company{}.

\section{Personal}
In my spare time, I enjoy time spent on various projects.
Often, these projects involve working with my hands to bring an idea to life.
What interests me the most about this, is the unique way working with my hands lets me think about problems very differently from my day-to-day work.
At the same time, it allows me to learn new skills, seldom seen today, while working towards a clear goal.
These projects have often involved building large furniture, or lamps, but have recently started moving into smaller items as well.
One of the most enjoyable parts of the project is the design process where I use 3D modelling software to create an initial draft.
Using this software is a skill I picked up in doing this hobby.

\hspace{7 mm} When I am not working on the next project, I instead enjoy climbing, something I have been doing for many years.

\vspace{0.5 cm}
I have been referred to this position by a former colleague and good friend, Gaia-Emilie Wiendel Madsen.
You can contact her on \href{mailto:gwm@novo.dk}{gwm@novo.dk} or +4527821147 for comment.

\input{../../content_files/input_files/greeting_and_signature}
\end{document}