\section{Motivation for Applying}
Hello, I am a Senior Data Scientist with a strong foundation in mathematics.
I excel at breaking down complex business problems into digestible mathematical statements, and making technically complex solutions accessible to stakeholders and colleagues with different backgrounds.
From all the good things I have heard, I believe \company{} could be the perfect fit, and I therefore wish to apply for the role as a \role{}. \newpar I have previously worked as a Data Scientist in the life-science sector during my time at RaySearch Laboratories.
I appreciated having a lasting impact on patient well-being and this is something I would like to do more of.
Therefore, I am motivated to transition from my current role as Senior Data Science Consultant at Valcon back into a position with more long-term engagements and meaningful impact. \newpar Lately, I have worked as a Senior Data Scientist in a consultancy role where I have applied my skills to a variety of problem domains.
Alongside this, I have spent a lot of my time mentoring junior colleagues and ensured the small data science team at Valcon has been developing in the right direction.
This is something I have come to greatly enjoy, and I value growing together with my colleagues. \newpar I am currently working on a machine learning model to enhance the quality of our client's invoicing process.
The project covers topics such as NLP, autoencoders, advanced custom training loops, and deployment of a real-time endpoint.
My blend of industry experience, and technical expertise would make me a great fit for this role.